### 2021-05-17 article/article.tex
update

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
%TODO: nsi intro, clear about factor 3
\section{Formalism}
\begin{align}
   \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align}
NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$.

For chirality $X \in \{L,R\}$, the NSI Hamiltonian takes the form 
\begin{align}
   H &= \frac{1}{2E} UM^2U^\dagger + \sqrt{2}G_F n_e \text{diag}(1,0,0) + \sqrt{2}G_F \sum_f n_f \epsilon^{fX}
\end{align}

We have no independent sensitivity for the chirality of $\epsilon^X$, so we sum over these and normalize the fermion number density $n_f$ by
the electron number density $n_e$. Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
so $n_u/n_e \simeq n_d/n_e \simeq 3$.
The effective matter NSI parameters now take the form
\begin{align} \label{eq:epsilon}
    \epsilon_{\alpha\beta} &= \sum_X \sum_f \frac{n_f}{n_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
                           &= \epsilon_{\alpha\beta}^{eV} + 3\epsilon_{\alpha\beta}^{uV} + 3\epsilon_{\alpha\beta}^{dV}
\end{align}
We note that our definition of $\epsilon_{\alpha\beta}$ differs from some texts, where the quark number density is used to normalize
the parameters\cite{deepcoreNSI}.

With the matter potential $V = \sqrt{2}G_F n_e$, we write
\begin{align} \label{eq:H_NSI}
   H &= \frac{1}{2E} UM^2U^\dagger + V\,
   \begin{bmatrix}
      1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
      \epsilon_{e\mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
      \epsilon_{e \tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
  \end{bmatrix}\,,
\end{align}
where we have assumed the components of the NSI matrix to be real.

@@

The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux at detector level for flavor $\beta$ as 
\begin{align}\label{eq:propFlux}
    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
\end{align}
where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
and flux level, we plot the oscillograms resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
and DeepCore track events originating from $\nm$ fluxes are contained. Starting with the $\nm$ flux ratio, we see that the only clear signal discernible to the IceCube detector
is a flux deficiency of a factor of $\sim 10^2$ from core-crossing neutrinos within a zenith range of $\ztrue > -0.87$. DeepCore on the other hand, 
observes multiple fringes of flux surpluses with a factor $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
energy-independent but zenith-sensetive IceCube deficiency.
%TODO: check values above after final plot of flux ratios
For the fluxes which drives cascades, we have to resort to the DeepCore detector alone. %TODO: fill more
Here we see a somewhat weaker signal, this time a zenith-independent deficiency. 
%TODO: fill with conclusion

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.8\linewidth]{figures/flux_ratio.pdf}
   \end{center}
   \caption{Ratio of detector NSI to SI atmospheric fluxes. We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
   Within the dotted (dashed) lines, 99\% of the  DeepCore (IceCube) MC events are contained. Since we limit our IceCube study to muon tracks,
   a dashed region is omitted in the left panel.}
\end{figure}%TODO:redo with more than 100x100. need high emt and log to show both cascade and track features at the same time.
%otherwise, the cascade ratio overpowers the track one.

@@

\section{Results}
%Short intro
\subsection{Methodology}\label{sec:method}
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.

For DeepCore and PINGU, and the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,. 
Since the median zenith is $\zreco = 0$ for DeepCore and PINGU, we allow the event count to rotate around zero.

We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$. We consider (best) worst-case scenarios in IceCube assuming
$(f=5\%)$, $f=15\%$. For PINGU, we use the same form but instead assume $f=0\%$ and $f=5\%$ for the best and worst-cases respecively. %TODO: maybe source/justification for these values?
For DeepCore, we use the provided systematic error distribution which accounts for uncertanties in the finite MC statistics and in the data-driven 
muon background estimate~\cite{DC2019data}.  %TODO segue

\subsection{Constraining the NSI parameters}
First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. We record the 
confidence levels in Table.~\ref{table:DC_PINGU_results} and best-fit points in Table ~\ref{table:bestfit}.

@@

% \begin{figure}[!tb]%TODO: redo this with P+/P-
% \begin{center}
%    \includegraphics[width=0.7\linewidth]{figures/Pmm_asymmetry.pdf}
% \end{center}
% \caption{Expected $\Delta \chi^2$ after three years of data.
%    $\dm$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
%    parameters other than the one shown in each panel are fixed to zero.}\label{fig:Pmm_asymmetry}
% \end{figure}

We can explain the asymmetry by looking looking at the oscillogram of the ratio $P(\emt^-)/P(\emt^+)$ in Fig.~\ref{fig:Pmm_asymmetry}, which is the $P_{\mu\mu}$ survival probability
given $\emt =-0.05$ divided by $P_{\mu\mu}$ for $\emt=0.05$. Muon events are the most abundant in IceCube and DeepCore/PINGU, and it suffices to study
$P_{\mu\mu}$ to explain the asymmetry. We see see that positive $\emt$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (pink area),
while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in the flux ratio plot, this muon survival abundance 
is indeed preserved at flux level.

\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.5\linewidth]{figures/emt_events.pdf}
   \end{center}
   \caption{The best-fit event count ratio at each detector for negative and positive $\emt$. PINGU shows promising 
   of distinguishing the sign of $\emt$, but favoring $\emt < 0$ while DeepCore has higher statistics for $\emt>0$ and a poor
   distinction for $\emt<0$}\label{fig:emt_events}%TODO: improve caption?
 \end{figure}
As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event count for $\emt=-0.02$ outnumber the event count with $\emt =0.05$ for
all bins except one, giving a high $\Delta \chi^2$ on both sides and slightly higher for $\emt=-0.02$. DeepCore on the other hand, 
has no bins where the event count for $\emt=-0.02$ surpasses the event count for $\emt=+0.02$, giving weak statistics for the negative side.

%TODO: ploit contour for ett-emt
{\renewcommand{\arraystretch}{1.3}
 \begin{table}
   \begin{center}
   \begin{tabular}{lcccc}
      \hline \hline \\
      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{4}{c}{IceCube}  \\
      $\emt$ & [-0.0098, 0.009 ] & [-0.0148, 0.014 ] & [-0.0152, 0.0145] & [-, -] \\\\
      & \multicolumn{4}{c}{DeepCore}  \\[0.3em]
      $\ett$ & [-0.029, 0.045] & [-, -]& [-0.029, 0.045] & [-, -] \\
      $\emt$ & [-0.015, 0.0048] & [-, 0.015]& [-0.015, 0.0048] & [-, 0.015] \\
      $\eem$ & [-0.072, 0.075] & [-0.132, 0.127]& [-0.072, 0.075] & [-0.132, 0.127]\\
      $\eet$ & [-0.074, 0.141] & [-0.174, 0.20  ]& [-0.074, 0.141] & [-0.174, 0.20  ]\\\\
      &\multicolumn{4}{c}{IceCube + DeepCore}  \\
      $\emt$ & [-0.0182,  0.00030] & [-, 0.0104] & [-0.0185, 0.00030] & [-, 0.0104] \\
      \hline
      \hline
   \end{tabular}
   \end{center}
   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. IceCube best and worst case refers to 
   the systematic uncertainty scenarios considered as in Sec.~\ref{sec:method}}\label{table:IC_DC_results}
\end{table}
\begin{table}
   \begin{tabular}{lcccc}
      \hline \hline \\
      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{4}{c}{PINGU} \\
      $\ett$ & [-0.0326, -] & [-0.0482, ] & [-0.0371, -] & [-, -] \\
      $\emt$ & [-0.0065, 0.0071] & [-0.011, 0.013] & [-0.0078, 0.0087] & [-0.0136, 0.0162] \\
      $\eem$ & [-0.062, 0.057] & [-0.122, 0.103] & [-0.1057, 0.0799] & [-0.198, 0.141]\\
      $\eet$ & [-0.069, 0.077] & [-0.121, 0.133] & [-0.1072, 0.1022] & [-0.1805, 0.1633]\\\\
      & \multicolumn{4}{c}{DeepCore + PINGU} \\
      $\ett$ & [-0.028, 0.043] & [-0.043, -] & [-0.0285,  0.0423] & [-0.0447, -]\\
      $\emt$ & [-0.0067, 0.0049] & [-0.0109,  0.0101] & [-0.0049, 0.0086] & [-0.0098, 0.0146]\\
      $\eem$ & [-0.048, 0.048]  & [-0.090, 0.085] & [-0.0721, 0.0503] & [-0.1262, 0.0931]\\
      $\eet$ & [-0.053, 0.072]  & [-0.101, 0.118] & [-0.0901, 0.0624] & [-0.1491, 0.1168]\\\\
      & \multicolumn{4}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ & [-0.0088,  0.003 ] & [-0.0128, 0.0081] & [-0.01, 0.0028] & [-0.0145, 0.0087]\\
      \hline
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. PINGU best and worst cases refers to 
   the systematic uncertainty scenarios considered as in Sec.~\ref{sec:method}}\label{table:PINGU_joint_results}
\end{table}

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}
%TODO:  include ranges for different f.
%make log table with secyions of dc, p, ic, dc+p
Comparing the PINGU results in Fig.~\ref{fig:PINGU_3D_NO} and the DeepCore results in Fig.~\ref{fig:DC_3D_NO}, we note that 
the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assumes no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in our joint analysis,
since PINGU has stronger statistics than DeepCore, and will thus pull the joint $\chi^2$ towards $\epsilon =0$.

>>>>

\usepackage{physics,amsmath, amsfonts, siunitx, amssymb, graphicx, subcaption}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\begin{document}
\section{Formalism}
Non-standard interactions are sub-leading contributions to neutrino flavor transitions arising from neutrino interactions with 
matter fermions not considered in the Standard Model. We consider matter NSIs arising from the neutral current NSIs, which exclude production 
and detection effects. An effective four-fermion Lagrangian for this type of interaction can be written as
\begin{align}
   \mathcal{L}_{\mathrm{NC}} &= -2 \sqrt{2} G_{F} \epsilon_{\alpha \beta}^{f X}\left(\bar{\nu}_{\alpha} \gamma^{\mu} P_{L} \nu_{\beta}\right)\left(\bar{f} \gamma_{\mu} P_{X} f\right)\,,
\end{align}
where NC denotes the neutral current interaction with 
$f \in \{e,u,d\}$, and $P_X$ is the chirality projection operators with $X \in \{L,R\}$.

For chirality $X$, the NSI Hamiltonian takes the form 
\begin{align}
   H &= \frac{1}{2E} UM^2U^\dagger + \sqrt{2}G_F n_e \text{diag}(1,0,0) + \sqrt{2}G_F \sum_f n_f \epsilon^{fX}
\end{align}

We have no independent sensitivity for the chirality of $\epsilon^X$, so we sum over these to obtain the vector part as $\epsilon^{fV}_{\alpha\beta} = \epsilon^{fL}_{\alpha\beta}+ \epsilon^{fR}_{\alpha\beta}$.
Moreover, we normalize the fermion number density $n_f$ by
the electron number density $n_e$. Our matter study will be wholly confined to the interior of the Earth, where we assume electrical neutrality and equal distribution of neutrons and protons, 
so we use the relations $n_u/n_e \simeq n_d/n_e \simeq 3$.
The effective NSI parameters in matter now take the form
\begin{align} \label{eq:epsilon}
    \epsilon_{\alpha\beta} &= \sum_{f,X} \frac{n_f}{n_e} \epsilon^{fX}_{\alpha\beta} \nonumber \\
                           &= \epsilon_{\alpha\beta}^{eV} + 3\epsilon_{\alpha\beta}^{uV} + 3\epsilon_{\alpha\beta}^{dV}
\end{align}
We note that our definition of $\epsilon_{\alpha\beta}$ differs from some texts, where the quark number density is used to normalize
the parameters\cite{deepcoreNSI}.

With the matter potential $V = \sqrt{2}G_F n_e$, we write
\begin{align} \label{eq:H_NSI}
   H &= \frac{1}{2E} UM^2U^\dagger + V\,
   \begin{bmatrix}
      1 + \epsilon_{ee} & \epsilon_{e\mu} & \epsilon_{e\tau}  \\
      \epsilon_{e\mu} & \epsilon_{\mu\mu} & \epsilon_{\mu\tau}  \\
      \epsilon_{e \tau} & \epsilon_{\mu\tau} & \epsilon_{\tau\tau}
  \end{bmatrix}\,,
\end{align}
where we have assumed the components of the NSI matrix to be real. To see the effect of a NSI, we have plotted a probability difference in the low energy range in Fig.~\ref{fig:Pmm_asymmetry}, and study
the flux ratio in Fig.~\ref{fig:flux_ratio}.

@@

The oscillation probability $P_{\alpha \beta}$ acts as a weight to the atmospheric flux, yielding the propagated flux at detector level for flavor $\beta$ as 
\begin{align}\label{eq:propFlux}
    \phi_\beta^\text{det} = \sum_\alpha P_{\alpha\beta} \phi_\alpha^\text{atm} \,,
\end{align}
where we sum over the initial lepton flavors $\alpha \in \{e,\mu, \bar{e}, \bar{\mu}\}$. To illustrate the impact of $\emt$ on both probability
and flux level, we plot the flux ratios resulting from Eq.~\ref{eq:propFlux} in Fig.~\ref{fig:flux_ratio}. In the left panel, we have marked the region in which 99\% of the 
DeepCore cascade events originating from $\ne$ and $\nt$ fluxes are contained. In the right panel, we show the two regions in which 99\% of the IceCube 
and DeepCore track events originating from $\nm$ fluxes are contained. Starting with the $\nm$ flux ratio, we see that the only clear signal discernible to the IceCube detector
is a flux deficiency of a factor of $\sim 10^2$ from core-crossing neutrinos within a zenith range of $\ztrue > -0.87$. DeepCore on the other hand, 
observes multiple fringes of flux surpluses with a factor $\sim 10$. The strongest surplus at \SI{20}{\GeV} is very weakly zenith dependent, a stark contrast to the
energy-independent but zenith-sensetive IceCube deficiency.
%TODO: check values above after final plot of flux ratios
For the fluxes which drives cascades, we have to resort to the DeepCore detector alone. %TODO: fill more
Here we see a somewhat weaker signal, this time a zenith-independent deficiency. 
%TODO: fill with conclusion

\begin{figure}[!tb]\label{fig:flux_ratio}
   \begin{center}
      \includegraphics[width=0.8\linewidth]{figures/flux_ratio.pdf}
   \end{center}
   \caption{Ratio of detector NSI to SI atmospheric fluxes. We set $\emt = -0.05$, and all other $\epsilon_{\alpha\beta}=0$. 
   Within the dotted (dashed) lines, 99\% of the  DeepCore (IceCube) MC events are contained. Since we limit our IceCube study to muon tracks,
   a dashed region is omitted in the left panel.}
\end{figure}% need high emt and log to show both cascade and track features at the same time.
%otherwise, the cascade ratio overpowers the track one.

@@

\section{Results}
In this section, we present the results from the experiments alone, as well as jointly. 
\subsection{Methodology}\label{sec:method}
For our analyses, we define our $\chi^2$ as
\begin{align} \label{eq:chisq}
    \chi^{2}(\hat{\theta},\alpha,\beta, \kappa)=\sum_{ijk} \frac{\left(N^\text{th}-N^\text{data}\right)_{ijk}^{2}}
    {\left(\sigma^\text{data}_{ijk}\right)^{2} + \left(\sigma^\text{syst}_{ijk}\right)^{2}}+ 
    \frac{(1-\alpha)^2}{\sigma_\alpha^2} + \frac{\beta^2}{\sigma_\beta^2}\,
\end{align}
where we minimize over the model parameters $\hat{\theta} \in \{\dm, \theta_{23}, \epsilon\}$, the penalty terms $\alpha$ and $\beta$, and the free parameter $\kappa$.
$N_{ijk}^\text{th}$ is the expected number of events from theory, and $N_{ijk}^\text{data}$ is the observed number of events in that bin. We set $\sigma_\alpha = 0.25$ as the atmospheric flux normalization error, and $\sigma_\beta = 0.04$ as the zenith angle slope error~\cite{hondapaper}. 
The observed event number has an associated Poissonian uncertainty $\sigma_{ijk}^\text{data} = \sqrt{N_{ijk}^\text{data}}$.
For IceCube, the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta (0.5 + \zreco_i )\right] N_{ijk}(\hat{\theta})\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:ICevents}. Here, we allow the event distribution to rotate around the median zenith angle of $\zreco = -0.5$.

For DeepCore and PINGU, and the event count takes the form
\begin{align}
    N^\text{th}_{ijk} = \alpha\left[1+\beta \zreco_i \right] N_{ijk}(\hat{\theta}) + \kappa N_{ijk}^{\mu_{atm}}\,,
\end{align}
with $N_{ijk}(\hat{\theta})$ from Eq.~\ref{eq:MCevents}. $N_{ijk}^{\mu_{atm}}$ is the muon background, which is left to float freely in the DeepCore analysis.
The background at PINGU can be considered neglible to first order~\cite{PINGUdata}, and we thus put $\kappa=0$ when calculating the PINGU $\chi^2$\,. 
For DeepCore and PINGU, the median zenith angle is $\zreco = 0$, we allow the event count to rotate around this point.

We treat the uncorrelated systematic uncertanties differently for each detector. For IceCube, we set $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$. We consider (best) worst-case scenarios in IceCube assuming
$(f=5\%)$, $f=15\%$. For PINGU, we use the same form but instead assume $f=0\%$ and $f=5\%$ for the best and worst-cases respecively. %TODO: maybe source/justification for these values?
For DeepCore, we use the provided systematic error distribution which accounts for uncertanties in the finite MC statistics and in the data-driven 
muon background estimate~\cite{DC2019data}. This is summarized in Table~\ref{table:syst_errors}.  %TODO segue
{\renewcommand{\arraystretch}{1.2}
\begin{table}
   \begin{tabular}{lcc}
      \hline \hline
      Experiment & Worst case & Best case \\
      \hline
      IceCube & $15\%$ & $5\%$ \\
      DeepCore & - & - \\
      PINGU & $5\%$ & $0\%$ \\
      \hline \hline
   \end{tabular}
   \caption{Definition of the worst and best case scenarios considered in each experiment, modelled by $\sigma_{ijk}^\text{syst} = f\sqrt{N_{ijk}^\text{data}}$ with $f$ from the table.
   We do not consider different DeepCore scenarios because the systematic error distribution there is already given in the data release~\cite{DC2019data}.}\label{table:syst_errors}
\end{table}

\subsection{Constraining the NSI parameters}
First, we set all standard oscillation parameters to their current best-fit values of Eq.~\ref{eq:PINGUparams}, except for $\dm$ and $\theta_{23}$, 
which we marginalize over their $3\sigma$ ranges of \SI{2.435e-3} to \SI{2.598e-3}{\electronvolt^2} and \SI{40.1} to \SI{51.7}{\degree} respectively. %TODO: make unit ranges nicer.
After the oscillation parameters have been marginalized out, we plot $\Delta \chi^2$ for each of the four NSI parameters in Fig.~\ref{fig:3D_NO}. We record the 
confidence levels in Table.~\ref{table:IC_DC_results} for DeepCore and IceCube, and best-fit points in Table ~\ref{table:bestfit}.

@@

To see the effect of a NSI at probability level, we plot the muon survival probability difference $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$, where 
$\epsilon^\pm_{\mu\tau} = \pm 0.05$ in Fig.~\ref{fig:Pmm_asymmetry}. We can explain the asymmetry in  by looking looking at the oscillogram. Muon events are the most abundant DeepCore/PINGU, and it suffices to study $P_{\mu\mu}$ to explain the asymmetry. 
We see see that positive $\emt$ generates a slightly higher $P_{\mu\mu}$ for energies around \SI{20}{\GeV} (blue area),
while negative $\emt$ produces higher $P_{\mu\mu}$ for almost all other combinations of ${\Etrue,\ztrue}$. As we see in Fig.~\ref{fig:flux_ratios}, this muon survival abundance 
is indeed preserved at flux level.

\begin{figure}[!tb]
\begin{center}
   \includegraphics[width=0.4\linewidth]{figures/Pmm_asymmetry.pdf}
\end{center}
\caption{The ratio $P_{\mu\mu}(\epsilon^+_{\mu\tau}) - P_{\mu\mu}(\epsilon^-_{\mu\tau})$ using  $\epsilon^\pm_{\mu\tau} = \pm 0.05$ in the DeepCore/PINGU energy range. Negative $\emt$ has the strongest signal, as the thin blue 
region stemming from $\emt = 0.05$ is less prominent than the red regions from $\emt=-0.05$.}\label{fig:Pmm_asymmetry}
\end{figure}
\begin{figure}[!tb]
   \begin{center}
      \includegraphics[width=0.4\linewidth]{figures/emt_events.pdf}
   \end{center}
   \caption{The best-fit event count ratio from each detector for $\emt = \pm 0.01$.}\label{fig:emt_events}%TODO: improve caption?
 \end{figure}
As we see in Fig.~\ref{fig:emt_events}, the binned PINGU event counts display strong differences for many bins, giving a high $\Delta \chi^2$ on both sides of $\emt=0$ and slightly higher for $\emt=-0.01$. DeepCore on the other hand, 
has fewer bins where the event count for $\emt=-0.01$ surpasses the event count for $\emt=+0.01$, giving weaker statistics for the negative side.

Comparing Fig.~\ref{fig:emt_events} with the flux ratios in Fig.~\ref{fig:flux_ratio}, we see that the reconstruction of PINGU is
superior to DeepCore, since the event ratio $\log{(N^+_{NSI}/N^-_{NSI})}$ (which is in reconstructed quantities) more closely matches the flux ratio $\log{(\phi_{NSI}/\phi_{SI})}$ (which is in true quantities).
This is most evident below \SI{20}{\GeV}, where the DeepCore reconstruction has washed out the fringes.

%TODO: ploit contour for ett-emt
{\renewcommand{\arraystretch}{1.3}
 \begin{table}
   \begin{center}
   \begin{tabular}{lcccc}
      \hline \hline
      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{4}{c}{IceCube}  \\
      $\emt$ & [-0.0098, 0.009 ] & [-0.0148, 0.014 ] & [-0.0152, 0.0145] & [-, -] \\\\
      & \multicolumn{4}{c}{DeepCore}  \\[0.3em]
      $\ett$ & [-0.029, 0.045] & [-, -]& [-0.029, 0.045] & [-, -] \\
      $\emt$ & [-0.015, 0.0048] & [-, 0.015]& [-0.015, 0.0048] & [-, 0.015] \\
      $\eem$ & [-0.072, 0.075] & [-0.132, 0.127]& [-0.072, 0.075] & [-0.132, 0.127]\\
      $\eet$ & [-0.074, 0.141] & [-0.174, 0.20  ]& [-0.074, 0.141] & [-0.174, 0.20  ]\\\\
      &\multicolumn{4}{c}{IceCube + DeepCore}  \\
      $\emt$ & [-0.0182,  0.00030] & [-, 0.0104] & [-0.0185, 0.00030] & [-, 0.0104] \\
      \hline
      \hline
   \end{tabular}
   \end{center}
   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. IceCube best and worst case refers to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}}\label{table:IC_DC_results}
\end{table}
\begin{table}
   \begin{tabular}{lcccc}
      \hline \hline
      Parameter & Best 90\% CL & Best $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{4}{c}{PINGU} \\
      $\ett$ & [-0.0326, -] & [-0.0482, ] & [-0.0371, -] & [-, -] \\
      $\emt$ & [-0.0065, 0.0071] & [-0.011, 0.013] & [-0.0078, 0.0087] & [-0.0136, 0.0162] \\
      $\eem$ & [-0.062, 0.057] & [-0.122, 0.103] & [-0.1057, 0.0799] & [-0.198, 0.141]\\
      $\eet$ & [-0.069, 0.077] & [-0.121, 0.133] & [-0.1072, 0.1022] & [-0.1805, 0.1633]\\\\
      & \multicolumn{4}{c}{DeepCore + PINGU} \\
      $\ett$ & [-0.028, 0.043] & [-0.043, -] & [-0.0285,  0.0423] & [-0.0447, -]\\
      $\emt$ & [-0.0067, 0.0049] & [-0.0109,  0.0101] & [-0.0049, 0.0086] & [-0.0098, 0.0146]\\
      $\eem$ & [-0.048, 0.048]  & [-0.090, 0.085] & [-0.0721, 0.0503] & [-0.1262, 0.0931]\\
      $\eet$ & [-0.053, 0.072]  & [-0.101, 0.118] & [-0.0901, 0.0624] & [-0.1491, 0.1168]\\\\
      & \multicolumn{4}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ & [-0.0088,  0.003 ] & [-0.0128, 0.0081] & [-0.01, 0.0028] & [-0.0145, 0.0087]\\
      \hline
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. PINGU best and worst cases refers to 
   the systematic uncertainty scenarios considered as in Table.~\ref{table:syst_errors}}\label{table:PINGU_joint_results}
\end{table}

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}
Comparing the PINGU results in Fig.~\ref{fig:PINGU_3D_NO} and the DeepCore results in Fig.~\ref{fig:DC_3D_NO}, we note that 
the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assumes no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in our joint analysis,
since PINGU has stronger statistics than DeepCore, and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
